Frozen Civil Conflicts

### 2024-03-11 paper.qmd
Add env variable to skip sbc

```{R}
#| label: fig-sbc
#| fig-cap: |
#|     Simulation based calibration results

sbc <- readRDS("./posteriors/sbc.rds") |>
    select(-.chain, -.iteration, -.draw)

>>>>

```{R eval = Sys.getenv("NO_SBC") == "" && file.exists("posteriors/sbc.rds")}
#| label: fig-sbc
#| fig-cap: |
#|     Simulation based calibration results
sbc <- readRDS("./posteriors/sbc.rds") |>
    select(-.chain, -.iteration, -.draw)
